---
title: "Final Paper"
author: "Rae Hoffman & Riley Shatz"
date: "12/11/2022"
output: pdf_document
references:
- id: zuckerman2012
  title: Why Is Reddit So Anti-Women? : An Epic Reddit Thread Counts the Ways
  author:
  - family: Zuckerman
    given: Esther
  publisher: The Atlantic
  type: article
  issued:
    year: 2012
- id: APA2018
  title: Harmful masculinity and violence
  author:
  type: article-journal
  publisher: American Psychological Association
    year: 2018
---
---

```{r, include = FALSE}
library(RedditExtractoR)
library(tidytext)
library(tm)
library(SnowballC)
library( reshape2 )
library( ggplot2 )
library( lattice )
library( rvest )
library( tidyverse )
library( SnowballC )
library( xml2 )
library( stringi )
```

## Introduction 

For this project we wanted to explore how men and women on Reddit discuss the opposite sex. Our initial thoughts/questions going into this were how do the members of these gender specific subreddits view the opposite sex and what type of words do they associate with them? Would women perhaps use phrases describing men’s personalities more, while men use phrases garnered towards women’s physical appearances? Are there more negative or positive words present? 

Our methods for exploring these potential differences were looking at two subreddits; TwoXChromosomes, which is a female dominated subreddit, and MensRights which is a male dominated subreddit. We started with TwoXChromosomes because we both were already familiar with it and knew it covered a range of topics and is also popular. Finding a perfect male-dominated subreddit for comparison was difficult in terms of finding an equal in regards to popularity and discussion points. We decided on MensRights because of its popularity and range of topics. While it is sort of an extreme example of men's discussion points, and fairly "meninist", we figured from the viewpoint of people pertaining more towards that view/side of things would see TwoXChromosomes as extreme. So they are both fairly extreme sides of the spectrum, but given their popularity, we figured they were both good examples of men and women's views on Reddit.  

## Data

To collect our data, we used RedditExtractoR. We first took the top posts from the last year, filtering by the keyword "men" for TwoXChromosomes subreddit. Then we took the text of all the posts and made it an object. We then turned the text into a corpus and cleaned things like punctuation, numbers, stopwords, etc. to then turn the corpus into a documenttermmatrix to faciliate our visualizations. We did the same process as below for the MensRights subreddit, with just the difference of using "women" as the keyword. 

```{r}
men.comments.xx <- find_thread_urls(keywords = "men",
  sort_by = "top",
  subreddit = "TwoXChromosomes",
  period = "year")

head(men.comments.xx$text)

alltext.XX <- men.comments.xx$text

#VectorSource interprets each element as a document & Corpus casts the result as a collection of documents
commentCorpus_xx <- Corpus( VectorSource(alltext.XX))
#We pipe the corpus through several tm_map() methods
commentCorpus_xx <- commentCorpus_xx %>%
  tm_map(removePunctuation) %>% ##eliminate punctuation
  tm_map(removeNumbers) %>% #no numbers
  tm_map(stripWhitespace) %>%#white spaces
  tm_map(tolower)%>% ##make all words lowercase
  tm_map(removeWords, c(stopwords("SMART"),"women","men","woman", "man", "male","female", "get", "dont", "just", "time", "edit", "like", "also", "don", "ive","lot","didnt","people")) 

#convert the corpus to a matrix to facilitate further analysis
commentCorpus_mat_xx <-as.matrix(TermDocumentMatrix( commentCorpus_xx ))
commentCorpus_wordFreq_xx <-sort(rowSums(commentCorpus_mat_xx), decreasing=TRUE)
```

```{r, include = FALSE}
#same process for MensRights subreddit
#extracting MensRights posts
xychrome <- find_thread_urls(keywords =  "women",
                                       subreddit = "MensRights",
                                       sort_by = "top",
                             period = "year")
head(xychrome$text)

alltext_mr <- xychrome$text

#clean text
commentCorpus_mr <- Corpus( VectorSource( alltext_mr ) )
commentCorpus_mr <- commentCorpus_mr %>%
  tm_map(removePunctuation) %>% 
  tm_map(removeNumbers) %>% 
  tm_map(stripWhitespace) %>%
  tm_map(tolower)%>% 
  tm_map(removeWords, c(stopwords("SMART"), "women", "men", "male", "female", "woman", "man", "get", "dont","just", "time", "edit","like","also", "people")) 

#tranform to matrix and get word freq
commentCorpus_mat_mr <-as.matrix(TermDocumentMatrix( commentCorpus_mr ))
commentCorpus_wordFreq_mr <-sort(rowSums(commentCorpus_mat_mr), decreasing=TRUE)

```


## Results

```{r}
#word frequency chart of women's comments about men
top15 <- commentCorpus_wordFreq_xx[1:15]

aplot <- as.data.frame( melt( top15 ) )
aplot$word <- dimnames( aplot )[[1]]
aplot$word <- factor(aplot$word,
                      levels=aplot$word[order(aplot$value,
                                               decreasing=F)])
fig <- ggplot(aplot, aes(x=word, y=value)) + 
  geom_bar(stat="identity",fill = "#e29578") + 
  xlab("Word Frquency in TwoXChromosone") + 
  ylab("Count") +
  coord_flip()
print(fig) 
```

```{r}
#word frequency chart of men's comments about women
top15 <- commentCorpus_wordFreq_mr[1:15]
aplot <- as.data.frame( melt( top15 ) )
aplot$word <- dimnames( aplot )[[1]]
aplot$word <- factor(aplot$word,
                      levels=aplot$word[order(aplot$value,
                                               decreasing=F)])
fig <- ggplot(aplot, aes(x=word, y=value)) + 
  geom_bar(stat="identity", fill = "") + 
  xlab("Word Frquency in MenRights") + 
  ylab("Count") +
  coord_flip()
print(fig)
```

What we were able to find was that in the women's based subreddit, TwoXXChromosome, women were more likely to discuss narratives and anecdotal experience when it came to men. They often used words like "feel",“make,” “told,” “wanted.” In the context of these words, often the women were speaking personal testimony on how men made them feel, their experiences with them, and often these experiences were negative. On the other hand, the men's rights subreddit reported a lot more factual, violent, and almost analytical language like "rape", “crime”, “violence”, “mass”, and “victims”. It seems as though when men talk about women, they are either speaking violently about them or speaking generally about violence towards women. 


### Analysis

Thinking into why we may have gotten the results we did, a big thing that came up was how we saw extreme ends of the spectrum of feelings vs. talk about violence. We think this could largely have to do with how Reddit offers users anonymity. This provides users the opportunity to speak without consequences, which could explain such a frequent number of violent words used against women on the MensRights subreddit. Since men on that subreddit do not have to think about repercussions from the language they use, they have a way to show their extreme views that they might not elsewhere. Another thing is that Redditors are mainly men, and it has been a long standing issue of Reddit being very anti-women. Zuckerman wrote an article in The Atlantic about a subreddit called "Why is Reddit so Anti-Women", which gained significant popularity and had many comments of women sharing their testimony to how they have been harassed on the platform due to being a woman [@Zuckerman2012]. This could definitely contribute to women on Reddit talking mainly about how men make them feel, vs. men on Reddit using anti-woman language, since Reddit has for many years been a place where women are harassed, and TwoXChromosomes gives them an avenue to vent. 

But what is the relationship between these differences outside of Reddit? To look into this we read an article from APA on harmful masculinity and violence, which discussed how men are socialized from an early age to express their distress and emotions in a violent manor, which then shifts to using violence to exert power over others, power that men are socialized to believe they are automatically entitled to. Whereas women are socialized to talk calmly about their distress and emotions and throughout life be calm and more submissive [@APA2018]. This research shows concepts and dynamics that we are all familiar with, and explains why we would see men speaking violently on Reddit whereas women talked about how men made them feel in a more calm manor. 

## Discussion

In conclusion, we can visually see a difference between men and women and their manner of speaking about each other in gender specific courses. Men and women have a different vocabulary when talking about each other in online circles. It seems like for women, they are telling stories and and experiences, and for men, they speak about current events and often violent occurrences. We believe that this is because Reddit, as an anonymous social media site, makes it easier for each gender to not only congregate based on similar viewpoints, experiences, and opinions, but allows them to share said opinions anonymously. In the analysis section, we were also able to discuss why men and women psychologically speak differently, because of their gender-norm-heavy socialization. 

In the future, it would be interesting to run a regression analysis to see if we can say with significance that men are more likely to use violent language against the opposite sex in comparison to women. Another helpful thing to study would be topic modeling, and see what topics were being discussed as well as gender. Lastly, we could perform a sentiment analysis to specifically define certain moods to certain words, which would help us analyze the moods that men and women have when speaking about one another. It might also be interesting to look at LGBTQ+ subreddits to see if different sexualities and gender spectrums are potrayed differently. 