---
title: "Final Paper"
author: "Rae Hoffman & Riley Shatz"
date: "12/11/2022"
output: pdf_document
---
---
title: "Fundamentals of Computing and Data Display"
subtitle: "Term paper template"
author: "Author"
date: "`r Sys.Date()`"
output:
  pdf_document:
    toc: yes
    df_print: kable
references:
- id: Wickham2014
  title: Tidy Data
  author:
  - family: Wickham
    given: Hadley
  container-title: Journal of Statistical Software
  volume: 59
  issue: 10
  page: 1-23
  type: article-journal
  issued:
    year: 2014
- id: Baumer2017
  title: Modern Data Science with R
  author:
  - family: Baumer
    given: Benjamin S.
  - family: Kaplan
    given: Daniel T.
  - family: Horton
    given: Nicholas J.
  type: book
  publisher: Chapman \& Hall/CRC Press.
  issued:
    year: 2017
---

```{r, include = FALSE}
library(knitr)
library(tidyverse)
```

## Introduction hey riley

For this project we wanted to explore how men and women on Reddit discuss the opposite sex. Our initial thoughts/questions going into this were how do the members of these gender specific subreddits view the opposite sex and what type of words do they associate them with? Would women perhaps use phrases describing men’s personalities more, while men use phrases garnered towards women’s physical appearances? Are there more negative or positive words present? 

Our methods for exploring these potential differences were looking at two subreddits; TwoXChromosomes, which is a female dominated subreddit, and MensRights which is a male dominated subreddit. We started with TwoXChromosomes because we both were already familiar with it and new it covered a range of topics and is popular. Finding a perfect male-dominated subreddit for comparison was difficult in terms of finding an equal in terms of popularity and discussion points. We decided on MensRights because of its popularity and range of topics. While it is sort of an extreme example of men's discussion points, and fairly "meninist", we figured from the viewpoint of people pertaining more towards that view/side of things would see TwoXChromosomes as extreme. So they are both fairly extreme sides of the spectrum, but given their popularity, we figured they were both good examples of men and women's views on Reddit.  

This section outlines the research idea. We can also cite related work here [@Wickham2014; @Baumer2017].

Note that compiled term paper (the PDF) is supposed to be more text-centered than the RMarkdown documents we used in class, i.e. the text sections are more detailed and big or redundant code chunks can be hidden.

## Data

This section describes the data sources and the data gathering process.

```{r}
# A code chunk that exemplifies the data gathering process
```

```{r, include = FALSE}
# Additional code chunks that repeat tasks or do basic things can be hidden
```

## Results

This section presents the main results.

### Analysis

Thinking into why we may have gotten the results we did, a big thing that came up was how we saw extreme ends of the spectrum of feelings vs. talk about violence. We think this could largely have to do with how Reddit offers users anonymity. This provides users the opportunity to speak without consequences, which could explain such a frequent number of violent words used against women on the MensRights subreddit. Since men on that subreddit do not have to think about repercussions from the language they use, they have a way to show their extreme views that they might not elsewhere. Another thing is that Redditors are mainly men, and it has been a long standing issue of Reddit being very anti-women. Zuckerman wrote an article in The Atlantic about a subreddit called "Why is Reddit so Anti-Women", which gained significant popularity and had many comments of women sharing their testimony to how they have been harassed on the platform due to being a woman [@Zuckerman2012]. This could definitely contribute to women on Reddit talking mainly about how men make them feel, vs. men on Reddit using anti-woman language, since Reddit has for many years been a place where women are harassed, and TwoXChromosomes gives them an avenue to vent. 

But what is the relationship between these differences outside of Reddit? To look into this we read an article from APA on harmful masculinity and violence, which discussed how men are socialized from an early age to express their distress and emotions in a violent manor, which then shifts to using violence to exert power over others, power that men are socialized to believe they are automatically entitled to. Whereas women are socialized to talk calmly about their distress and emotions and throughout life be calm and more submissive [@APA2018]. This research shows concepts and dynamics that we are all familiar with, and explains why we would see men speaking violently on Reddit whereas women talked about how men made them feel in a more calm manor. 

## Discussion

This section summarizes the results and may briefly outline advantages and limitations of the work presented.

## References
